\texttt{SuperScreen}: An open-source package for simulating the magnetic response of two-dimensional superconducting devices

### 2021-11-24 main.tex

Here we assume an out-of-plane applied magnetic field $\vec{H}_\mathrm{applied}(\vec{r}')=H_\mathrm{z,\,\mathrm{applied}}(\vec{r}')\hat{z}$. $F$ is the film area (with $g = 0$ outside of the film), and $Q_x(\vec{r},\vec{r}')$, $Q_y(\vec{r},\vec{r}')$, and $Q_z(\vec{r},\vec{r}')$ are dipole kernel functions which give the respective component of the magnetic field at position $\vec{r}=(x, y, z)$ due to a dipole of unit strength at position $\vec{r}'=(x', y', z')$:
\begin{align}
    \label{eq:kernels}
    \begin{split}
        Q_x(\vec{r}, \vec{r}') &=  3\frac{(x-x')(z-z')}
        {4\pi[(z-z')^2+\rho^2]^{5/2}}\\
        Q_y(\vec{r}, \vec{r}') &=  3\frac{(y-y')(z-z')}
        {4\pi[(z-z')^2+\rho^2]^{5/2}}\\
        Q_z(\vec{r}, \vec{r}') &=  \frac{2(z-z')^2-\rho^2}
        {4\pi[(z-z')^2+\rho^2]^{5/2}},
    \end{split}
\end{align}
where $\rho=\sqrt{(x-x')^2 + (y-y')^2}$.

@@

@@

In scanning superconducting quantum interference device (SQUID) susceptometry, the diamagnetic susceptibility of a superconducting sample is measured by bringing the sample close to a pair of superconducting loops~\cite{Gardner2001-gr, Huber2008-il, Kirtley_Kalisky_2012}. The first loop, called the ``pickup loop" (PL) is attached to a SQUID circuit that sensitively measures the magnetic flux threading the loop. The second loop, called the ``field coil" (FC), carries a known current $I_\mathrm{FC}$ and applies a known magnetic field to both the pickup loop and the sample. The superconducting sample screens the magnetic field from the field coil, modifying the amount of flux threading the pickup loop. Thus the mutual inductance $M_\mathrm{PL-FC}$ between the field coil and pickup loop in the presence of a sample provides a measure of the sample's magnetic susceptibility. For superconducting samples, this diamagnetic response is a measure of the sample's penetration depth and therefore its superfluid density.

@@

Having established the value of the field coil - pickup loop mutual inductance $M_\text{PL-FC, no sample}$ in the absence of a sample, we can simulate a scanning SQUID susceptometry measurement by calculating $M_\mathrm{PL-FC}$ in the presence of a superconducting sample as a function of the relative position of the pickup loop and the sample. For example, in Figure~\ref{fig:squid-susc} we simulate a SQUID susceptometry measurement of a ``Large'' susceptometer (the sample) measured with a ``Medium'' suceptometer (the sensor). Given a \inline{Device} representing the sensor and a \inline{Device} representing the sample, this calculation is performed in three steps:
\begin{enumerate}
    \item{Simulate the sensor with some known current $I_\mathrm{FC}$ circulating in the field coil to obtain \inline{field_coil_solution} and $M_\text{PL-FC, no sample}$.}
    \item{For a given relative position $(x_s, y_s)$ between the sensor and sample, simulate the sample with an applied field given by \inline{field_coil_solution.field_at_position()} to obtain \inline{sample_solution}.}
    \item{Simulate the sensor again, this time with the applied field given by \inline{sample_solution.field_at_position()}, and evaluate the fluxoid $\Phi^f_\mathrm{PL}$ for the hole representing the sensor's pickup loop, and calculate the mutual inductance: $M_\mathrm{PL-FC}(x_s, y_s)=\Phi^f_\mathrm{PL} / I_\mathrm{FC}$.}
\end{enumerate}
These three steps are repeated for every desired $(x_s, y_s)$ to build up a susceptometry image. The susceptibility signal is reported as $M_\text{PL-FC}(x_s, y_s) - M_\text{PL-FC, no sample}$, where values that are more negative indicate a stronger diamagnetic response from the sample. Note that in principle it is possible to combine the sensor and sample into a single \inline{Device} with 6 superconducting layers, however this is impractical because it would require generating a new mesh for each $(x_s, y_s)$ and, as discussed in detail in \ref{appendix:numerics}, the problem scales unfavorably with the number of layers in a device and with the total lateral extent of a device.

@@

@@

% As mentioned in Section~\ref{section:model:multilayer}, at each iteration of this process, we update the applied field $H_{z,\,\mathrm{applied}}(\vec{r}, z_\ell)$ at each layer $\ell$ based on the currents flowing in all other layers $m\neq\ell$, according to

% \begin{align}
% \begin{split}
%     &H_{z,\,\mathrm{applied}}(\vec{r}, z_\ell) \to\\
%     &H_{z,\,\mathrm{applied}}(\vec{r}, z_\ell)
%     + \sum_{m\neq\ell}
%     \int_{S_m} Q_z(\vec{r},\vec{r}')g_m(\vec{r}')\,\mathrm{d}^2r',
%     \label{eq:iterative}
% \end{split}
% \end{align}
% where $S_m$ is surface of all films in layer $m$ and $g_m$ is the stream function for layer $m$.
% Furthermore, for a model with $L$ layers, at each iteration, Eq.~\ref{eq:iterative} requires the calculation of $\binom{L}{2} = L(L-1)/2$ such kernel matrices. representing $Q_z(\vec{r},\vec{r}')$ in Eq.~\ref{eq:hz-from-kernel}, each of which is a dense $p\times t$ floating point matrix. Typically the number of mesh vertices is approximately half the number of triangles ($p\approx t / 2$), so for a mesh with $t=10,000$ triangles, each of these $\mathbf{Q_z}$ matrices is roughly 400 MB (200 MB) if using 64-bit double-precision floats (32-bit single-precision floats). Furthermore, each iteration requires performing $2\binom{L}{2} = L(L-1)$ sums involving $\mathbf{Q_z}\cdot\mathbf{g}_m$, where $\mathbf{g}_m$ is the $n\times1$ vector defining the stream function in layer $m$ evaluated at the center of each triangle in the mesh.

% To avoid redundant computation at each iteration and running out of memory during the iterative process, the $\mathbf{Q_z}$ matrices are computed once during the first iteration, cached to a temporary directory on disk, and loaded from disk during subsequent iterations, such that only a single $\mathbf{Q_z}$ is in memory at any given time. If running \SuperScreen on a machine with both hard disk (HDD) and solid state disk (SSD) storage, one should ensure that Python uses a temporary directory located on a solid state disk to avoid a significant performance penalty due to hard disk read/write speeds. See the documentation for the \inline{tempfile} module of the Python standard library for more details. Both the amount of computation needed per iteration and the number of iterations required to reach a certain level of convergence (quantified, for example, by the fractional change in flux through each polygon in the model from one iteration to the next)

>>>>

Here we assume an out-of-plane applied magnetic field $\vec{H}_\mathrm{applied}(\vec{r}')=H_\mathrm{z,\,\mathrm{applied}}(\vec{r}')\hat{z}$. $F$ is the film area (with $g = 0$ outside of the film), and $Q_x(\vec{r},\vec{r}')$, $Q_y(\vec{r},\vec{r}')$, and $Q_z(\vec{r},\vec{r}')$ are dipole kernel functions which give the respective component of the magnetic field at position $\vec{r}=(x, y, z)$ due to a dipole of unit strength at position $\vec{r}'=(x', y', z')$:
\begin{align}
    \label{eq:kernels}
    \begin{split}
        Q_x(\vec{r}, \vec{r}') &=  3\frac{(x-x')(z-z')}
        {4\pi[(z-z')^2+\rho^2]^{5/2}}\\
        Q_y(\vec{r}, \vec{r}') &=  3\frac{(y-y')(z-z')}
        {4\pi[(z-z')^2+\rho^2]^{5/2}}\\
        Q_z(\vec{r}, \vec{r}') &=  \frac{2(z-z')^2-\rho^2}
        {4\pi[(z-z')^2+\rho^2]^{5/2}},
    \end{split}
\end{align}
where $\rho=\sqrt{(x-x')^2 + (y-y')^2}$. Eq.~\ref{eq:field_from_kernel} can also be seen as the Biot-Savart Law formulated in terms of the stream function $g$.

@@

\subsection{Calculating inductance}
\label{section:examples:inductance}

@@

In scanning superconducting quantum interference device (SQUID) susceptometry, the magnetic susceptibility of a sample is measured by bringing the sample close to a pair of superconducting loops~\cite{Gardner2001-gr, Huber2008-il, Kirtley_Kalisky_2012}. The first loop, called the ``pickup loop" (PL) is attached to a SQUID circuit that sensitively measures the magnetic flux threading the loop. The second loop, called the ``field coil" (FC), carries a known current $I_\mathrm{FC}$ and applies a known magnetic field to both the pickup loop and the sample. A superconducting sample will screen the magnetic field from the field coil, modifying the amount of flux threading the pickup loop and reducing the mutual inductance $M_\mathrm{PL-FC}$. The magnitude of this reduction in $M_\mathrm{PL-FC}$ is a measure of the sample's penetration depth and therefore its superfluid density.

@@

Having established the value of the field coil - pickup loop mutual inductance in the absence of a sample, $M_\text{PL-FC, no sample}$, we can simulate a scanning SQUID susceptometry measurement by calculating $M_\mathrm{PL-FC}$ in the presence of a superconducting sample as a function of the relative position of the pickup loop and the sample, $(x_s, y_s)$. For example, in Figure~\ref{fig:squid-susc} we simulate a SQUID susceptometry measurement of a ``Large'' susceptometer (the sample) measured with a ``Medium'' suceptometer (the sensor). Given a \inline{Device} representing the sensor and a \inline{Device} representing the sample, this calculation is performed in three steps:
\begin{enumerate}
    \item{Simulate the sensor with some known current $I_\mathrm{FC}$ circulating in the field coil to obtain \inline{field_coil_solution} and $M_\text{PL-FC, no sample}$.}
    \item{For a given relative position $(x_s, y_s)$ between the sensor and sample, simulate the sample with an applied field given by \inline{field_coil_solution.field_at_position()} to obtain \inline{sample_solution}.}
    \item{Simulate the sensor again, this time with the applied field given by \inline{sample_solution.field_at_position()}, and evaluate the fluxoid $\Phi^f_\mathrm{PL}$ for the hole representing the sensor's pickup loop, and calculate the mutual inductance: $M_\mathrm{PL-FC}(x_s, y_s)=\Phi^f_\mathrm{PL} / I_\mathrm{FC}$.}
\end{enumerate}
These three steps are repeated for every desired $(x_s, y_s)$ to build up a susceptometry image. The susceptibility signal is reported as $M_\text{PL-FC}(x_s, y_s) - M_\text{PL-FC, no sample}$, where values that are more negative indicate a stronger diamagnetic response from the sample. Note that in principle it is possible to combine the sensor and sample into a single \inline{Device} with 6 superconducting layers, however this is impractical because it would require generating a new mesh for each $(x_s, y_s)$ and, as discussed in detail in \ref{appendix:numerics}, the problem scales unfavorably with the number of layers in a device and with the total lateral extent of a device.

@@

\section{Acknowledgements}
\label{section:acknowledgements}
Some of the computing for this project was performed on the Sherlock cluster. We would like to thank Stanford University and the Stanford Research Computing Center for providing computational resources and support that contributed to these research results. We acknowledge useful discussions with John R. Kirtley.

@@
